---
title: "Assignment 4 - Tidy data"
subtitle: '2030071 - 1753320'
author: "Group 50: Romée Simons and Tycho Brouwer"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: cosmo
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#the needed packages are: 
library(tidyverse)
library(patchwork)
library(plotly)
library(ggdist)
library(kableExtra)
library(tidyr)
library(plyr)

set.seed(30250) #makes sure random numbers are reproducible

```

# Task 1

For importing the data set, **;** was used as the delimiter, the first 4 lines were skipped, and the final line was skipped by setting the maximum lines read.

Also, the decimal mark was correctly set by setting the locale using the **,** decimal mark.

The data for the **Subject**, the years, are in the character format because they where recognized as the column titles.

The column containing the value **scale** for all it's entries is missing a value.

The column names should be **Subject**, **Year**, and **Score**.

```{r, load data, message=FALSE}
happiness_data <- read_delim(
  'dataset_happiness.csv',
  delim=";",
  show_col_types = FALSE,
  skip = 4,
  n_max = 6,
  locale=locale(decimal_mark = ",")
  ) |> glimpse()
```

# Task 2

```{r}

happiness_data_long <- happiness_data |>
  pivot_longer(cols = `2013`:`2022`,
               names_to = "Year",
               values_to = "Score") |>
  rename(c("...2"="ScoreType")) |>
  glimpse()
```

# Task 3

```{r}
happiness_data_long |>
  ggplot(aes(Year, Score, colour = Subject, group = Subject)) +
  geom_path() +
  ggtitle("Trend of happiness over years") +
   theme_minimal()
```

# Task 4

```{r}
temp_data_wide <- read_delim(
  'data_temp_wide.csv',
  show_col_types = FALSE,
  delim = ","
  )

head(temp_data_wide, 5)
glimpse(temp_data_wide)
```

# Task 5

```{r}
temp_data_pivoted <- temp_data_wide |>
  pivot_longer(
    cols = city_lower:city_upper,                    # columns to make long 
    names_to = c("ValueType"), # new column names for headers
    names_prefix = "city_",
    values_to = "Temp"                # new column name for values
  )

glimpse(temp_data_pivoted)
```

# Task 6

```{r}
temp_data_separated <- temp_data_pivoted |>
  separate(col=`Temp`, into = c("City", "Temp"), sep = "_", convert = TRUE)

glimpse(temp_data_separated)
```












