---
title: "Assignment - Reproducible Workflows"
subtitle: "1753320 - 2030071"
author: "Tycho Brouwer and Romée Simons"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: cosmo
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
bibliography: refs.bib
csl: apa.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(reprores)
library(tibble)
library(kableExtra)
library(cli)
library(ggplot2)
library(tidyverse)
```

# Task 1 

## Tycho Brouwer

### Education

- VWO NT&NG **(2015-2021)**
- Bsc. Mechanical Engineering \@ TU/e **(2021-now)**

### Employment

- Sailing instructor **(2018-2023)**

### Hobbies

- Badminton at Panache
- Homelab tickering
- Programming

## Romée Simons

### Education

- Gymnasium EM **(2018-2023)**
- Pre University College \@ University of Leiden **(2021-2023)**
- Bsc. Psychology & Technology \@ TU/e  **(2023-now)**

### Employment

- Ice cream shop **(summer 2023)**
- Tutoring high school subjects **(2020-2023)**
- Lyceo tutor **(2024-now)**

### Hobbies 

- Reading
- Rowing and Running
- Spending time with friends & family

# Task 2

To generate normally distributed values use the `rnorm(n, mean, std)` function from the `stats` package.

```{r fifteen random values, echo=FALSE}
rnorm(15, 0, 1)
```

# Task 3

To add a footnote you can type '^' followed by text in square brackets '[]' ^[This is a footnote for task 3]

\

A horizontal rule can be added by typing `---`

---

\

> A blockquote can be added by typing the '>' directly followed by the quote.

# Task 4

```{r display histogram}
data("pets", package = "reprores")
ggplot(pets, aes(age)) +
  geom_histogram(binwidth = 1, fill = "lightblue") +
  labs(
    caption = "Histogram of the pet ages from the reprores dataset"
  )
```

# Task 5

To read the data, use the function `read_csv()` from the `tidyverse` package. To calculate the average use the function `mean()`.

```{r average age, echo=FALSE}
pets <- read_csv("https://psyteachr.github.io/reprores/data/pets.csv", show_col_types = FALSE)
```

The average age of the pets is `r mean(pets$age)`.

# Task 6

```{r summary, echo=FALSE}
table <- pets %>%
  group_by(country) %>%
  summarise(
    n = n(),
    weight = mean(weight), 
    age = mean(age)  
  ) # Creating data and table 

kable(table, 
      digits = 2, 
      col.names = c("Country", "N", "Weight", "Age"),
      caption = "Table 1: Summary statistics for the pets dataset.") |>
  kable_classic(full_width = FALSE, font_size = 20) |>
  kable_styling(full_width = FALSE) |>
  add_header_above(c(" " = 2, "Means" = 2)) # Making the table look nice
```

# Task 7

Do not forget to include hobbies in [task number 1](#task-1). The above was made using the Rmarkdown package [@Baumer].
